\Large \bf New Static Analysis Techniques to Detect Entropy Failure Vulnerabilities

### 2018-12-12 paper/paper.tex
bib
paper branch

@@

@@

>>>>

In this section we describe the background necessary to understand our new approach.

Test reference: \cite{GKW18}

@@

\subsection{Naive Approaches}

Before we cover our approach to this problem we will briefly discuss a number of approaches that do not work, but build to our final result.

A first attempt to solve this problem might include running taint analysis on each version $P_1$ and $P_2$ of the program. However, since
taint analysis merely provides an overapproximation to this problem, this approach is necessarily unsound. Instead, we would like to view
this as a $2$-safety property:

@@

\bibliographystyle{alpha}
\bibliography{refs}
